Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
placeholder abstract

\textbf{Abstract---}
We develop techniques for automated reasoning about end-to-end properties of
abstract network topologies, and embody them in a network synthesis tool called
\sysname. \sysname allows network operators to write a high-level routing policy
over an abstraction of their network topology. From such a specification,
\sysname synthesizes a collection of router configurations running the
distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
centralized routing policy for any concrete instantiation of the abstract
topology, and for any combination of network failures in the resulting concrete
topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as
reachability between a source and destination under k-failures, are also
guaranteed to hold under any concrete instantiation of the abstract topology.
%
Something something, expandable/incremental networks. Something something scales
compilation to large networks. Something something, templates easier to
understand.
%These strong guarantees allow operators to reason about the routing behavior of
%their network at a high-level abstraction, while also generating an efficient
%low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any
%way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ({\large $*$}). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertise the route to all of its peers ($*$). For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.

>>>>

\textbf{Abstract---}
\ryan{Copied from conclusion for reference}
We develop \sysname, the first system that can generate device configuration templates for large networks from high-level specifications of network topology and policy. \sysname is based on new abstractions for capturing parameterized network topologies, and their evolution, and algorithms to analyze the combined impact of topology and routing policy on the network's fault tolerance. Our analysis operates entirely in the abstract domain and guarantees correctness for all concrete instantiations of the topology. Experiments with many types of real-world topologies and policies show that our abstractions and analysis are precise and that, for large networks, configuration synthesis is two orders of magnitude faster than systems that operate over concrete topologies.

%We develop techniques for automated reasoning about end-to-end properties of
%abstract network topologies, and embody them in a network synthesis tool called
%\sysname. \sysname allows network operators to write a high-level routing policy
%over an abstraction of their network topology. From such a specification,
%\sysname synthesizes a collection of router configurations running the
%distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
%centralized routing policy for any concrete instantiation of the abstract
%topology, and for any combination of network failures in the resulting concrete
%topology.
%
%Additionally, properties proven by \sysname over the abstract topology, such as
%reachability between a source and destination under k-failures, are also
%guaranteed to hold under any concrete instantiation of the abstract topology.
%
%Something something, expandable/incremental networks. Something something scales
%compilation to large networks. Something something, templates easier to
%understand.
%These strong guarantees allow operators to reason about the routing behavior of
%their network at a high-level abstraction, while also generating an efficient
%low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any
%way, so long as the new resulting topology also respects the abstraction.
%
%We test \sysname out on ... blah blah blah

@@

%By combining the tagging, filtering and preference mechanisms, we can generate safe BGP configurations. In general, configurations are generated by combining the per-prefix configurations in the same order specified in the policy.
Figure~\ref{fig:bgp-configs} shows part of the final configuration for spine routers for the concrete and abstract policies in a vendor-neutral syntax.
%
For prefix $\True$ ($0.0.0.0/[0..32]$), the spine routers will match advertisements from peer N1 and N2. The match for N1 is preferred since it has a higher BGP local-preference attribute (110). If an advertisement from N1 is available the spine uses this and attaches the community tag $(1,0)$ before sending the route to all its peers ($*$). If an advertisement is only available from the backup N2, then it attaches the tag $(0,1)$ instead.
%
The template configuration matches any global prefix $\CD{\$GP}$ from any internal peer and re-advertises the route to all of its peers. For any local prefix it will allow an advertisement from any internal peer, and re-advertise the route to only other internal peers. The concrete configurations have a similar configuration for each local and global prefix.
